Universal Anonymous Signatures

### 2022-09-13 prism-backend/research/gsac/formal-uas.tex
Updated correctness.
Updated GS-MDO and DAC appendices.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
      \rbrace_{i\in[n]}) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[ht!]
    \centering
    \scalebox{0.9}{

@@

      \end{minipage}
    }
    \scalebox{0.9}{

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[htp!]
    \centering
    \scalebox{0.9}{

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\cid,\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.9}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OExt}(\parm) \\
%         (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \gets
%         \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         \trans[\cid_i]) \\
%         \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\usk,\ATTR[\cid],\lbrace \cid_i \rbrace_{i \in [n]},
%         \lbrace\attrs_i\rbrace_{i \in [n]}) = 0: \\
%         \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

@@

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.9}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OId}(\parm) \\
%         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor \cred \in \scred: \\
%         \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
%         \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
%         \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
%         \pcind \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OAnon,\OBTCHALb} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
%       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
%         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\Oforgeissue}(\parm) \\
%         \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
%         \pcreturn 0 \\
%         \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
%         \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
%         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
%         \gets \ExtractIssue(\trap,\utrans) \\
%         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         % \trans[\cid_i]) \\
%         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
%         \rbrace_{i\in[n]}) \neq \yissue:
%         \pcreturn 1 \\
%         \pcif \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup \CU:
%         \pcreturn 1 \\
% %        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
% %        \uid \in \HU \cup \CU: \pcreturn 1 \\
% %        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
%         \pcreturn 0
%       }
%       \vspace*{0.5em}

    % \end{minipage}    
    % \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
        (\parm,\trap) \gets \Setup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]: \pcreturn 0 \\
        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
        \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
        = 0: \pcreturn 1 \\
        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
        % \pcreturn 0
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        \pcif \exists i\in[n]~\suchthat~
        \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
        \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
        \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
        \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
        (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
        \pcind \pcreturn 1 \\        
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg)
        \neq \yinsp \lor \yinsp \neq \yinsp':
        \pcreturn 1 \\
%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
        \pcreturn 1 \\        
        \pcreturn 0        
      }      
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{figure}[htp!]  
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \in \HU: % \land
      %(\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.
    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\WREG,\OBTAIN,\SIGN$.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.9}{
    \input{figures/nizk-ring.tex}
  }
  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for \CUASGenHideIss.}
  \label{fig:nizk-ring}
\end{figure}

@@

Modelling-wise, this requires to replace the \Sign and \Verify functions with
a single $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets \langle
\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval) \rangle$,
where $\utrans_{\Sig}$ is the transcript of the protocol, and is logged now in
an equivalent of the \SIG table (\CSIG for challenge transcripts). The \SIGN
and \CHALb oracles now also accept a random value from the adversary, but
are otherwise adapted in the natural way, where the signer is always honest, but
the verifier is played by the adversary (e.g., similar to the \OBTAIN oracle).

>>>>

\begin{figure}[ht!]
  \centering  
  \scalebox{0.85}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
      \rbrace_{i\in[n]}) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[ht!]
    \centering
    \scalebox{0.85}{

@@

      \end{minipage}
    }
    \scalebox{0.85}{

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[htp!]
    \centering
    \scalebox{0.85}{

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.85}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval \lor \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\cid,\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \textrm{Parse}~\PUBOK[\oid]~\textrm{as}~((\cdot,\finsp),\cdot) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.85}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OExt}(\parm) \\
%         (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \gets
%         \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         \trans[\cid_i]) \\
%         \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\usk,\ATTR[\cid],\lbrace \cid_i \rbrace_{i \in [n]},
%         \lbrace\attrs_i\rbrace_{i \in [n]}) = 0: \\
%         \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

@@

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.85}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OId}(\parm) \\
%         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor \cred \in \scred: \\
%         \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
%         \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
%         \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
%         \pcind \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.85}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OAnon,\OBTCHALb} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.85}{
    \begin{minipage}[t]{\textwidth}
%       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
%         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\Oforgeissue}(\parm) \\
%         \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
%         \pcreturn 0 \\
%         \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
%         \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
%         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
%         \gets \ExtractIssue(\trap,\utrans) \\
%         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         % \trans[\cid_i]) \\
%         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
%         \rbrace_{i\in[n]}) \neq \yissue:
%         \pcreturn 1 \\
%         \pcif \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup \CU:
%         \pcreturn 1 \\
% %        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
% %        \uid \in \HU \cup \CU: \pcreturn 1 \\
% %        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
%         \pcreturn 0
%       }
%       \vspace*{0.5em}

    % \end{minipage}    
    % \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]: \pcreturn 0 \\
        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
        \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
        = 0: \pcreturn 1 \\
        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
        % \pcreturn 0
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        \pcif \exists i\in[n]~\suchthat~
        \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
        \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
        \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
        \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
        (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
        \pcind \pcreturn 1 \\        
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg)
        \neq \yinsp \lor \yinsp \neq \yinsp':
        \pcreturn 1 \\
%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
        \pcreturn 1 \\        
        \pcreturn 0        
      }      
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{figure}[htp!]  
  \centering
  \scalebox{0.85}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \in \HU: % \land
      %(\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.
    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\WREG,\OBTAIN,\SIGN$.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

@@

\begin{figure}[ht!]
  \scalebox{0.85}{
    \input{figures/nizk-ring.tex}
  }
  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for \CUASGenHideIss.}
  \label{fig:nizk-ring}
\end{figure}

@@

Modelling-wise, this requires to replace the \Sign and \Verify functions with
an interactive protocol $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets
\langle\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval)
\rangle$,
where $\utrans_{\Sig}$ is the transcript of the protocol, and is logged now in
an equivalent of the \SIG table (\CSIG for challenge transcripts). The \SIGN
and \CHALb oracles now also accept a random value from the adversary, but
are otherwise adapted in the natural way, where the signer is always honest, but
the verifier is played by the adversary (e.g., similar to the \OBTAIN oracle).

### 2022-09-13 prism-backend/research/gsac/introduction-paper.tex
Updated GS-MDO and DAC appendices.

A crucial aspect to cater for all possible variants that we aim to subsume, is
the incorporation of ``functional placeholders'' enabling customisation. We
introduce abstract functions whose computation needs to be proven correct by the
user. Depending on the choice of these functions, one can instantiate a
different related scheme, which is anyway secure according to our \UAS model.
We also allow to modulate the information to be revealed after signing time,
with the information revealed at signing time, allowing policies such as
``deanonymize only if 18+ years old''.

>>>>

% A crucial aspect to cater for all possible variants that we aim to subsume, is
% the incorporation of ``functional placeholders'' enabling customisation. We
% introduce abstract functions whose computation needs to be proven correct by the
% user. Depending on the choice of these functions, one can instantiate a
% different related scheme, which is anyway secure according to our \UAS model.
% We also allow to modulate the information to be revealed after signing time,
% with the information revealed at signing time, allowing policies such as
% ``deanonymize only if 18+ years old''.
